### 2017-07-06 paper/exp_appendix.tex
table cleaned

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments
} \\\hline
{aaron2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{ax} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{complex} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{counterex1b} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{cousot9} & {0.08} & {yes} & {3} & {yes} & {no
} \\\hline
{easy2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{loops} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{nestedloop} & {0.09} & {yes} & {3} & {yes} & {no
} \\\hline
{perfect1} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{random1d} & {0.08} & {yes} & {2} & {yes} & {yes
} \\\hline
{realbubble} & {0.18} & {yes} & {3} & {yes} & {yes
} \\\hline
{realheapsort} & {0.18} & {no} & {} & {no} & {no
} \\\hline
{realheapsort\_step1} & {0.09} & {no} & {} & {no} & {no
} \\\hline
{realselect} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{rsd} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{sipma91} & {0.11} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedDis1} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedFails1} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedFails4} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedNestedMultipleDep} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedpldi3} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedSimpleMultiple} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{speedSingleSingle} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{terminate} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet0} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wise} & {0.07} & {no} & {} & {no} & {no} \\\hline 
    \end{tabular}
    \caption{Additonal experimental results for benchmarks from~\cite{ADFG10:lexicographic} extended with probabilistic loops and/or probabilistic assignments.}
    \label{tab:exp3}
\end{table}
\end{center}

>>>>

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments
} \\\hline
{aaron2} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{ax} & {0.09} & {yes} & {3} & {yes} & {yes} \\\hline
{complex} & {0.08} & {yes} & {1} & {yes} & {yes} \\\hline
{counterex1b} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{cousot9} & {0.08} & {yes} & {3} & {yes} & {no} \\\hline
{easy2} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{loops} & {0.08} & {no} & {} & {no} & {no} \\\hline
{nestedloop} & {0.09} & {yes} & {3} & {yes} & {no} \\\hline
{perfect1} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{random1d} & {0.08} & {yes} & {2} & {yes} & {yes} \\\hline
{realbubble} & {0.18} & {yes} & {3} & {yes} & {yes} \\\hline
{realheapsort} & {0.18} & {no} & {} & {no} & {no} \\\hline
{realheapsort\_step1} & {0.09} & {no} & {} & {no} & {no} \\\hline
{realselect} & {0.09} & {yes} & {3} & {yes} & {yes} \\\hline
{rsd} & {0.08} & {yes} & {1} & {yes} & {yes} \\\hline
{sipma91} & {0.11} & {yes} & {2} & {yes} & {yes} \\\hline
{speedDis1} & {0.07} & {no} & {} & {no} & {no} \\\hline
{speedFails1} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{speedFails4} & {0.07} & {no} & {} & {no} & {no} \\\hline
{speedNestedMultipleDep} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{speedpldi3} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{speedSimpleMultiple} & {0.08} & {no} & {} & {no} & {no} \\\hline
{speedSingleSingle} & {0.09} & {yes} & {2} & {yes} & {yes} \\\hline
{terminate} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{wcet0} & {0.09} & {yes} & {2} & {yes} & {yes} \\\hline
{wcet2} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{wise} & {0.07} & {no} & {} & {no} & {no} \\\hline 
    \end{tabular}
    \caption{Additonal experimental results for benchmarks from~\cite{ADFG10:lexicographic} extended with probabilistic loops and/or probabilistic assignments.}
    \label{tab:exp3}
\end{table}
\end{center}

### 2017-07-06 paper/experiments.tex
changes to experiments
table cleaned

\section{Experimental Results}
We have implemented our algorithm (in C++) and present two sets of experimental results.
For all the experimental results we use Aspic~\cite{} for invariant generation, 
and our algorithm requires linear-programming solution for which we use CPlex~\cite{}.
Our experimental results were obtained on [SPEC OF COMPUTER].

@@

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments
} \\\hline
{alain} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{catmouse} & {0.06} & {yes} & {2} & {yes} & {yes
} \\\hline
{counterex1a} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{counterex1c} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{easy1} & {0.07} & {yes} & {1} & {yes} & {yes
} \\\hline
{exmini} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{insertsort} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{ndecr} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{perfect} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{perffect2} & {0.1} & {yes} & {3} & {yes} & {no
} \\\hline
{real2} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{realheapsort\_step2} & {0.07} & {yes} & {1} & {no} & {no
} \\\hline
{realshellsort} & {0.07} & {yes} & {1} & {no} & {no
} \\\hline
{serpent} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{sipmabubble} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedDis2} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedFails2} & {0.06} & {yes} & {2} & {yes} & {no
} \\\hline
{speedNestedMultiple} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedpldi2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedpldi4} & {0.07} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedSimpleMultipleDep} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedSingleSingle2} & {0.08} & {yes} & {2} & {yes} & {no
} \\\hline
{unperfect} & {0.08} & {yes} & {2} & {yes} & {no
} \\\hline
{wcet1} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{while2} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline

@@

{Variables} & {LOC} & {Inv Time (s)} & {Our Time (s)} & {Total Time (s)} \\\hline
{2} & {20} & {0.050189} & {0.028366} & {0.078555} \\\hline
{3} & {32} & {0.060078} & {0.02359} & {0.083668} \\\hline
{4} & {56} & {0.074388} & {0.030035} & {0.104423} \\\hline
{5} & {104} & {0.131122} & {0.051545} & {0.182667} \\\hline
{6} & {200} & {0.354702} & {0.097943} & {0.452645} \\\hline
{7} & {392} & {1.30833} & {0.29947} & {1.6078} \\\hline
{8} & {776} & {7.55238} & {0.69566} & {8.24804} \\\hline
{9} & {1544} & {33.0638} & {2.4977} & {35.5615} \\\hline
{10} & {3080} & {164.088} & {8.763} & {172.851} \\\hline
{11} & {6152} & {817.914} & {35.37} & {853.284} \\\hline
{12} & {12296} & {4260.96} & {145.18} & {4406.14} \\\hline
\end{tabular}
\caption{Experimental results for synthetic examples.}\label{tab:exp2}
\end{table}
\end{center}

>>>>

\section{Experimental Results}\label{sec:experiments}
We have implemented our algorithm (in C++) and present two sets of experimental results.
For all the experimental results we use Aspic~\cite{} for invariant generation, 
and our algorithm requires linear-programming solution for which we use CPlex~\cite{}.
Our experimental results were obtained on [SPEC OF COMPUTER].

@@

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments} \\\hline
{alain} & {0.09} & {yes} & {2} & {yes} & {yes} \\\hline
{catmouse} & {0.06} & {yes} & {2} & {yes} & {yes} \\\hline
{counterex1a} & {0.08} & {no} & {} & {no} & {no} \\\hline
{counterex1c} & {0.09} & {yes} & {3} & {yes} & {yes} \\\hline
{easy1} & {0.07} & {yes} & {1} & {yes} & {yes} \\\hline
{exmini} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{insertsort} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{ndecr} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{perfect} & {0.09} & {yes} & {3} & {yes} & {yes} \\\hline
{perffect2} & {0.1} & {yes} & {3} & {yes} & {no} \\\hline
{real2} & {0.07} & {no} & {} & {no} & {no} \\\hline
{realheapsort\_step2} & {0.07} & {yes} & {1} & {no} & {no} \\\hline
{realshellsort} & {0.07} & {yes} & {1} & {no} & {no} \\\hline
{serpent} & {0.08} & {yes} & {1} & {yes} & {yes} \\\hline
{sipmabubble} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{speedDis2} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedFails2} & {0.06} & {yes} & {2} & {yes} & {no} \\\hline
{speedNestedMultiple} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline
{speedpldi2} & {0.07} & {yes} & {2} & {yes} & {yes} \\\hline
{speedpldi4} & {0.07} & {yes} & {3} & {yes} & {yes} \\\hline
{speedSimpleMultipleDep} & {0.07} & {no} & {} & {no} & {no} \\\hline
{speedSingleSingle2} & {0.08} & {yes} & {2} & {yes} & {no} \\\hline
{unperfect} & {0.08} & {yes} & {2} & {yes} & {no} \\\hline
{wcet1} & {0.09} & {yes} & {2} & {yes} & {yes} \\\hline
{while2} & {0.08} & {yes} & {3} & {yes} & {yes} \\\hline

@@

{Variables} & {LOC} & {Inv Time (s)} & {Our Time (s)} & {Total Time (s)
} \\\hline
{0} & {8} & {0.09} & {0.02} & {0.11} \\\hline
{1} & {14} & {0.05} & {0.02} & {0.07} \\\hline
{2} & {20} & {0.06} & {0.03} & {0.08} \\\hline
{3} & {32} & {0.07} & {0.03} & {0.09} \\\hline
{4} & {56} & {0.08} & {0.04} & {0.11} \\\hline
{5} & {104} & {0.14} & {0.06} & {0.19} \\\hline
{6} & {200} & {0.36} & {0.1} & {0.46} \\\hline
{7} & {392} & {1.31} & {0.3} & {1.61} \\\hline
{8} & {776} & {7.56} & {0.7} & {8.25} \\\hline
{9} & {1544} & {33.07} & {2.5} & {35.57} \\\hline
{10} & {3080} & {164.09} & {8.77} & {172.86} \\\hline
{11} & {6152} & {817.92} & {35.37} & {853.29} \\\hline
{12} & {12296} & {4260.96} & {145.18} & {4406.14} \\\hline
\end{tabular}
\caption{Experimental results for synthetic examples.}\label{tab:exp2}
\end{table}
\end{center}
